Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
rewrite meta-estimator part, no longer a subsection

Building on the core interface introduced in the previous section, we now
present in this section advanced API mechanisms for building meta-estimators,
composing complex estimators and then selecting models.

\subsection{Meta-estimators}

In machine learning, some algorithms are expressed as meta-algorithms built
and parametrized on simpler algorithms. Examples include ensemble methods which
build and combine several simpler models (e.g., decision trees), or multiclass
and multilabel classification schemes which can be used to turn a binary
classifier into a multiclass or multilabel classifier. In \sklearn, such algorithms are
implemented as \textit{meta-estimators}. They take as input an existing base
estimator and use it internally for learning and making predictions.

@@

>>>>

Some machine learning algorithms are expressed naturally
as meta-algorithms parametrized on simpler algorithms.
Examples include ensemble methods which
build and combine several simpler models (e.g., decision trees), or multiclass
and multilabel classification schemes which can be used to turn a binary
classifier into a multiclass or multilabel classifier. In \sklearn, such algorithms are
implemented as \textit{meta-estimators}. They take as input an existing base
estimator and use it internally for learning and making predictions.
All meta-estimators implement the regular estimator interface.

@@

Since using meta-estimators requires the construction of nested objects,
the decision to implement a meta-estimator
rather than fold the behavior it implements
into existing estimators classes
is always based on a trade-off between genericity and ease of use.
Relating to the example just given,
all \sklearn classifiers are designed to do multiclass classification
and the use of the \texttt{multiclass} module
is only necessary in advanced use cases.
